More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
smalltypo

\subsection{Running example}
- Detail of a $\tau$* sequence, \\
- construction of the predicate\\
- defn / elimination of the intermediaite variables\\
- construction of the weak OT.

\noindent
$\ostate{1000}\OTarrow{m\_rec(m,x), \phi_1 = [x=s_1\_b \land
    m=s_1\_m]}\ostate{2100}$\\
$\qquad\ostate{2100}$ variables: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2100}\OTarrow{\tau <m\_send(m_1\_m,m_1\_x), r\_rec(?m',?b)>,
  \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
$\qquad\ostate{2001}$ variables: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
...\}$;\\
\\
$\ostate{2001}\OTarrow{v,
  \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
$\qquad\ostate{2002}$ variables: $\psi_3 = \{r_2\_b:=r_1\_b\}$;\\

>>>>

\subsection{Running example}
- Detail of a $\tau^*$ sequence, \\
- construction of the predicate\\
- defn / elimination of the intermediaite variables\\
- construction of the weak OT.

The ``saturation'' step in the construction of the weak relation will
pick all $\tau^*$ and $\tau^*;a$ sequences from the OA, and build a weak
OT from each sequence. Here is one example:

\noindent
$\ostate{1000}\OTarrow{m\_rec(m,x), \phi_1 = [x=s_1\_b \land
    m=s_1\_m]}\ostate{2100}$\\
$\qquad\ostate{2100}$ variables: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2100}\OTarrow{\tau <m\_send(m_1\_m,m_1\_x), r\_rec(?m',?b)>,
  \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
$\qquad\ostate{2001}$ variables: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
; s_2\_b:=s_1\_b\}$;\\
\\
$\ostate{2001}\OTarrow{v,
  \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
$\qquad\ostate{2002}$ variables: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\
